Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-08 conclusions.tex
Minor rewording in conclusion
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@968 ccdd05d5-56c1-461a-bf98-85f6876523b4
Adding line on comp det stat
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@972 ccdd05d5-56c1-461a-bf98-85f6876523b4

We have demonstrated a computationally feasible procedure for the rapid and even preemptive
detection of gravitational waves emitted during the coalescence of neutron
stars and stellar-mass black holes. Our method is as fast as standard \fft{}
convolutions but allows for sample-in-sample-out processing.
Our search targets are expected to
produce prompt electromagnetic signals and may be the progenitors of some short
hard gamma-ray bursts.  Rapid alerts to the broader astronomical community will
improve the chances of detecting an electromagnetic counterpart in bands from
gamma-rays down to radio.  We anticipate requiring $\sim100$ modern
multi-core computers to analyze a four-detector network of gravitational-wave data
for binary neutron stars and stellar-mass black holes.  This is well within the
current computing capabilities of the \LIGO{} Data Grid~\cite{LDG}.

@@

\editorial{Should we mention composite detection?}
\editorial{Yes, although only as something else that we could employ to further reduce compuational cost.}

>>>>

We have demonstrated a computationally feasible procedure for the rapid and
even preemptive detection of gravitational waves emitted during the coalescence
of neutron stars and stellar-mass black holes. Our method is as fast as
standard \fft{} convolutions but allows for zero latency, sample-in-sample-out
operation.  Our search targets are expected to produce prompt electromagnetic
signals and may be the progenitors of some short hard gamma-ray bursts.  Rapid
alerts to the broader astronomical community will improve the chances of
detecting an electromagnetic counterpart in bands from gamma-rays down to
radio.  We anticipate requiring $\sim100$ modern multi-core computers to
analyze a four-detector network of gravitational-wave data for binary neutron
stars and stellar-mass black holes.  This is well within the current computing
capabilities of the \LIGO{} Data Grid~\cite{LDG}. In the future, this could be
improved upon further by conditionally reconstructing the \SNR{} time-series
only during times when a composite dection statistic crosses a
threshold~\cite{svd-compdetstat}.

@@
